Stack Safety is a Security Property

### 2021-04-17 tex/main.tex
Dealing with lazy policies

We find that Roessler and Dehon's {\em Depth Isolation} micro-policy, in
which memory cells within each stack frame are tagged with the identity of
the function activation that owns the frame and access to those locations is
then permitted only when that activation is currently executing, validates our
stepwise properties.  On the other hand, testing reveals their more efficient
\emph{Lazy Tagging} policy does not enforce step-wise integrity. In fact
we reason that both of their lazy policies violate the temporal aspect of confidentiality in
corner cases where data can leak across repeated calls to the same callee,
and \emph{Lazy Tagging and Clearing} also violates integrity in these instances.\apt{is this
  right?? I though Lazy tagging was fully ok, and lazy tagging + clearing violated
  temporal confidentialitty (only).}\sna{I was wrong about that. It's true of lazy tagging
  (provided the caller initializes their frame) but not lt+c}We
propose a variant of {\em Lazy Tagging and Clearing} that \emph{should} enforce
confidentiality, albeit at some performance cost.
%
\ifaftersubmission
\bcp{Did Nick and Andre know about this deficiency?  Did they mention
  it in their paper?  (If neither, we should make a bigger deal out of the
  fact that we discovered it.)\apt{Their paper is a little vague on this subject.
    They refer to ``temporal security properties'' as something to do with dangling
    pointers, but they don't define it.
    Then they say that Depth Isolation has weaker temporal security
    guarantees than Static Authorities (tag=function name), but they don't explain why
    (and I don't see why). They don't say anything explicit about the temporal
    security properties of Lazy Tagging and Clearing, but they consider it to enforce
    a completely different (and generally weaker) policy anyway (``data flow
    integrity'' vs. ``memory safety'').}}\bcp{Sigh.  OK, I propose that we
  leave this issue to deal with later (in consultation with them, which we
  don't have time to do a good job of today).  At any rate, by my reading we
are not saying anything incorrect at the moment.}
\fi

@@

{\em Lazy Per-activation Tagging and Clearing} ends up enforcing the combination
of deferred stepwise stack integrity and stepwise confidentiality---we
don't actually need a deferred confidentiality property here. Therefore,
it also enforces observational stack safety, so we declare it stack safe.\apt{Ugh.
  We haven't set up this definition clearly enough (nor should we try).}
Our properties have allowed us to reject an enforcement mechanism as
not really stack safe, and describe a fix.

>>>>

We find that Roessler and Dehon's {\em Depth Isolation} micro-policy, in
which memory cells within each stack frame are tagged with the identity of
the function activation that owns the frame and access to those locations is
then permitted only when that activation is currently executing, validates our
stepwise properties. On the other hand, we reason that \emph{Lazy Tagging and Clearing}
violates the temporal aspect of confidentiality in
corner cases where data can leak across repeated calls to the same callee,
and also violates integrity if the leak happens to use the caller's frame. We
propose a variant of {\em Lazy Tagging and Clearing} that \emph{should} enforce
confidentiality, albeit at some performance cost.
%
\ifaftersubmission
\bcp{Did Nick and Andre know about this deficiency?  Did they mention
  it in their paper?  (If neither, we should make a bigger deal out of the
  fact that we discovered it.)\apt{Their paper is a little vague on this subject.
    They refer to ``temporal security properties'' as something to do with dangling
    pointers, but they don't define it.
    Then they say that Depth Isolation has weaker temporal security
    guarantees than Static Authorities (tag=function name), but they don't explain why
    (and I don't see why). They don't say anything explicit about the temporal
    security properties of Lazy Tagging and Clearing, but they consider it to enforce
    a completely different (and generally weaker) policy anyway (``data flow
    integrity'' vs. ``memory safety'').}}\bcp{Sigh.  OK, I propose that we
  leave this issue to deal with later (in consultation with them, which we
  don't have time to do a good job of today).  At any rate, by my reading we
are not saying anything incorrect at the moment.}
\fi

@@

We believe that {\em Lazy Per-activation Tagging and Clearing}, in which
each activation is tagged uniquely, ends up enforcing the combination
of deferred stepwise stack integrity and stepwise confidentiality.
This is because tags that persist between calls will not become active again.
Our properties have allowed us to reject an enforcement mechanism as
not really stack safe, and describe a potential fix that itself is a
prime candidate for future testing.
